---
title: "Assignment 7"
format: html
editor: visual
---

```{r}
#| output: false
library(tidyverse)
```

## Task 1

First I created longer iris dataset using pivot_longer

```{r}
iris_longer <- pivot_longer(iris, cols = -Species, names_to = "Trait", values_to = "Size")
```

## Task 2

### 2.1

Here I make groups containing 4 measurements for each species and then make summary of mean sizes

```{r}
task_21 <- iris_longer %>%
  group_by(Species,Trait) %>%
  summarise(mean_size = mean(Size, na.rm = TRUE))
```

### 2.2

Here I make similar groups to 2.1 and then filter Species col by two given with addition of max col and put it inside summarise function to show only top values for each group

```{r}
task_22 <- iris_longer %>%
  group_by(Species,Trait) %>%
  filter(Species %in% c("virginica","versicolor")) %>%
  summarise(Max = max(Size))
```

### 2.3

Lastly I once again group by Species and Traits, next I add col for a mean values (as suggested in task) and filter out rows which Size is less then mean. Finally I count remaining rows for each group

```{r}
task_23 <- iris_longer %>% 
  group_by(Species,Trait) %>%
  mutate(mean_size = mean(Size)) %>% 
  filter(Size > mean_size) %>% 
  count(Species, Trait)
```
