---
title: "Assignment 8"
format: html
editor: visual
---

## Original plot

```{r,fig.width=12,fig.align='center',fig.height=15,echo=FALSE,message=FALSE,warning=FALSE}
load("~/Raport project/15.RData")
library(ggplot2)
library(dplyr)
library(tidyr)
library(plotly)

fig1 <- plot_ly(wykres_combined_10, x = ~Length, y = ~MHC_I_alpha1, text = ~Species,
                type = 'scatter', mode = 'markers',
                size = ~MHC_I_alpha1, color = ~Species,
                marker = list(sizemode = 'diameter'),
                legendgroup = ~Species) %>%
  layout(
         xaxis = list(title = "Assembly length"),
         yaxis = list(title = "Number of Alpha 1 hits"))

fig2 <- plot_ly(wykres_combined_10, x = ~Length, y = ~MHC_I_alpha2, text = ~Species,
                type = 'scatter', mode = 'markers',
                size = ~MHC_I_alpha2, color = ~Species,
                marker = list(sizemode = 'diameter'),
                legendgroup = ~Species,
                showlegend = FALSE) %>%
  layout(
         xaxis = list(title = "Assembly length"),
         yaxis = list(title = "Number of Alpha 2 hits"))

fig3 <- plot_ly(wykres_combined_10, x = ~Length, y = ~MHC_I_alpha3, text = ~Species,
                type = 'scatter', mode = 'markers',
                size = ~MHC_I_alpha3, color = ~Species,
                marker = list(sizemode = 'diameter'),
                legendgroup = ~Species,
                showlegend = FALSE) %>%
  layout(
         xaxis = list(title = "Assembly length"),
         yaxis = list(title = "Number of Alpha 3 hits"))

subplot(fig1, fig2, fig3, nrows = 3, margin = 0.05, titleX = TRUE, titleY = TRUE) %>%
  layout(legend = list(x = 1.5, y = 0, xanchor = "right", yanchor = "bottom"))
```

## Fixed plot

```{r,fig.width=12,fig.align='center',fig.height=15,echo=FALSE,message=FALSE,warning=FALSE}

library(stringr)

# Dodanie nowej kolumny z grupą
wykres_combined_10 <- wykres_combined_10 %>%
  mutate(SpeciesGroup = word(Species, 1))

# fig1
fig1 <- plot_ly(wykres_combined_10,
                x = ~Length,
                y = ~MHC_I_alpha1,
                text = ~Species,
                type = 'scatter',
                mode = 'markers',
                size = ~MHC_I_alpha1,
                color = ~SpeciesGroup,
                legendgroup = ~SpeciesGroup) %>%
  layout(
    xaxis = list(title = "Assembly length"),
    yaxis = list(
      title = list(text = "Number of Alpha 1 hits", standoff = 20),
      automargin = TRUE
    )
  )

# fig2
fig2 <- plot_ly(wykres_combined_10,
                x = ~Length,
                y = ~MHC_I_alpha2,
                text = ~Species,
                type = 'scatter',
                mode = 'markers',
                size = ~MHC_I_alpha2,
                color = ~SpeciesGroup,
                legendgroup = ~SpeciesGroup,
                showlegend = FALSE) %>%
  layout(
    xaxis = list(title = "Assembly length"),
    yaxis = list(
      title = list(text = "Number of Alpha 2 hits", standoff = 20),
      automargin = TRUE
    )
  )

# fig3
fig3 <- plot_ly(wykres_combined_10,
                x = ~Length,
                y = ~MHC_I_alpha3,
                text = ~Species,
                type = 'scatter',
                mode = 'markers',
                size = ~MHC_I_alpha3,
                color = ~SpeciesGroup,
                legendgroup = ~SpeciesGroup,
                showlegend = FALSE) %>%
  layout(
    xaxis = list(title = "Assembly length"),
    yaxis = list(
      title = list(text = "Number of Alpha 3 hits", standoff = 20),
      automargin = TRUE
    )
  )

# Połączenie wykresów
subplot(fig1, fig2, fig3, nrows = 3, margin = 0.05, titleX = TRUE, titleY = TRUE) %>%
  layout(
    legend = list(x = 1.5, y = 0.5, xanchor = "right", yanchor = "upper")
  )

```

Main changes:

1.  Size of circles is now smaller to not repeat information and to make it more visible
2.  Legend is grouped by main species name so it is not overwhelming and easier to distinguish
3.  Plot is wider making it less compressed
4.  Specific species names are shown when pointed on specific circles

Additional information could be presented on different plots to keep them simple and clean.

### Code changes inside plots

```{r echo=TRUE,eval=FALSE}
# creating species groups
wykres_combined_10 <- wykres_combined_10 %>%
  mutate(SpeciesGroup = word(Species, 1))

# applying it to plots instead of ~Species
color = ~SpeciesGroup,
legendgroup = ~SpeciesGroup

#removed 
marker = list(sizemode = 'diameter')

#legend changed from 
layout(legend = list(x = 1.5, y = 0, xanchor = "right", yanchor = "bottom"))
#to
legend = list(x = 1.5, y = 0.5, xanchor = "right", yanchor = "upper")

```
